True versus apparent shapes of astrophysical bow shocks

### 2016-05-17 papers/Paper1/sec-application.tex
Add table to paper of arc parameters from fits

\section{Application to proplyd bowshocks}
\label{sec:application}

\defcitealias{Canto:1996}{CRW}
\newcommand\CRW{\citetalias{Canto:1996}}

@@

\subsection{\CRW{} Scenario}
This scenario can be described with the formalism of
\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
solution for the two winds interaction problem in the thin shell
approximation, in terms of a free parameter
$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
momentum ratio, which the quantities with subindex 1 corresponds to
the strongest wind, therefore $\beta<=1$.

@@

\subsubsection{Methodology}
Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta^1 ~C$. For the shell's position, the marks were placed in the outer border of each shock. 
The number of marks used in each shell varies with shell's size, and with our confidence with our measurements.
Thus, we used few points in small bow shocks and/our the bow shock's outer shell is not well defined. The distance $D$ is measured as the distance between the position of $\theta^1 ~C~Ori$ 
and each proplyd's position. The radius of curvature $R_c$ is measured as the radius of the 
best circle fit of all the data points taken for each proplyd's shell. Finally, we measure $R_0$ as the distance between the proplyd's position and the circle's border in the line which 
include the center of curvature.
To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, and made 10 sets of randomly chosen removed marks, and made the measurements again to 
see how much these ``variations'' deviates from the original data. The results are summarized and explained in figure (\ref{fig:prop-shell-rad}).  In this figure, in the left side, for each source, 
the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing 2/3 of the marks, but always keeping at least four points. 
In the better observed shells such as 177-341 (top row), the circle
fits are relatively robust to removing points, resulting in little variation between the subsamples. 
But also there are cases where the variations are more noticeable.

@@

\begin{figure*}
\includegraphics[width=\linewidth]{../../proplyd-wind-figs/plot-wind-fits}
\label{fig:pressure}
\caption{Up: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd. The gray line represents the stellar flux at the distance $D$. Down: In colored lines, estiamted stagnation pressure for each proplyd. 
The gray solid line represent the stellar wind at the distance $D$. in both cases, the big dots represent the variations which have more agreement with ionization balance and pressure balance, respectively.}
\end{figure*}
%Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with fixed wind's momentum ratio $\beta$. 
%The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
%curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
%with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.

>>>>

\section{Application to proplyd bowshocks}
\label{sec:application}
\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}
\newcommand\CRW{\citetalias{Canto:1996}}

@@

\subsection{\CRW{} Scenario}
\label{sec:crw-scenario}
This scenario can be described with the formalism of
\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
solution for the two winds interaction problem in the thin shell
approximation, in terms of a free parameter
$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
momentum ratio, which the quantities with subindex 1 corresponds to
the strongest wind, therefore $\beta<=1$.

@@

\subsubsection{Methodology}
\label{sec:methodology}
Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta^1 ~C$. For the shell's position, the marks were placed in the outer border of each shock. 
The number of marks used in each shell varies with shell's size, and with our confidence with our measurements.
Thus, we used few points in small bow shocks and/our the bow shock's outer shell is not well defined. The distance $D$ is measured as the distance between the position of $\theta^1 ~C~Ori$ 
and each proplyd's position. The radius of curvature $R_c$ is measured as the radius of the 
best circle fit of all the data points taken for each proplyd's shell. Finally, we measure $R_0$ as the distance between the proplyd's position and the circle's border in the line which 
include the center of curvature.
To estimate the uncertainties of our measurements, we remove a fraction of the shell's marks, and made 10 sets of randomly chosen removed marks, and made the measurements again to 
see how much these ``variations'' deviates from the original data. The results are summarized and explained in figure (\ref{fig:prop-shell-rad}).  In this figure, in the left side, for each source, 
the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing 2/3 of the marks, but always keeping at least four points. 
In the better observed shells such as 177-341 (top row), the circle
fits are relatively robust to removing points, resulting in little variation between the subsamples. 
But also there are cases where the variations are more noticeable.

@@

\begin{figure}
\includegraphics[width=\linewidth]{../../proplyd-wind-figs/plot-wind-fits}
\label{fig:pressure}
\caption{Up: In colored lines,  the required ionizing flux to balance the photoevaporated flow for each proplyd. The gray line represents the stellar flux at the distance $D$. Down: In colored lines, estiamted stagnation pressure for each proplyd. 
The gray solid line represent the stellar wind at the distance $D$. in both cases, the big dots represent the variations which have more agreement with ionization balance and pressure balance, respectively.}
\end{figure}

\begin{table*}
  \caption{Fitted arc parameters for proplyd bowshocks}
  \label{tab:arc-fits} 
\newcommand\C[1]{\multicolumn{1}{c}{#1}}
\begin{tabular}{llrllllrlll}\toprule
             &          & \multicolumn{3}{c}{\dotfill Observed \dotfill}              & \multicolumn{6}{c}{\dotfill Model fits \dotfill} \\ 
  \C{OW}     & \C{Name} & \(D'\) &\C{ \(R_0'/D'\) }&\C{ \((R_c'/R_0')_{\mathrm{shape}}\) }&\C{ \((R_c'/R_0')_{\mathrm{flux}}\) }&\C{ \(\beta\) }&\C{ \(\xi\) }&\C{ \(|i|\) }&\C{ \(D\) }&\C{ \(R_0/D\)}\\
  \C{(1)}& \C{ (2) }&\C{ (3)    }&\C{    (4)      }&\C{              (5)           }&\C{           (6)             }&\C{     (7)   }&\C{   (8)   }&\C{   (9) }&\C{  (10) }&\C{   (11)} \\
\midrule     
168-328  &     & 6.8 & \(0.152 \pm 0.001\) & \(1.42 \pm 0.09\) & \(1.45 \pm 0.05\) & \(0.018 \pm 0.003\) & 0.4--0.6 & \(33 \pm 3\) & \(0.017 \pm 0.001\) & \(0.115 \pm 0.005\)\\
169-338  &     & 16.5 & \(0.059 \pm 0.001\) & \(1.76 \pm 0.48\) & \(1.50 \pm 0.05\) & \(0.002 \pm 0.001\) & 0.8--0.8 & \(43 \pm 8\) & \(0.049 \pm 0.006\) & \(0.035 \pm 0.005\)\\
177-341  & HST1& 25.6 & \(0.144 \pm 0.001\) & \(1.21 \pm 0.02\) & \(1.21 \pm 0.02\) & \(0.018 \pm 0.003\) & 0.1--0.2 & \(30 \pm 5\) & \(0.064 \pm 0.003\) & \(0.115 \pm 0.005\)\\
180-331  &     & 25.1 & \(0.061 \pm 0.007\) & \(1.30 \pm 0.04\) & \(1.27 \pm 0.05\) & \(0.003 \pm 0.001\) & 0.4--0.4 & \(35 \pm 7\) & \(0.067 \pm 0.007\) & \(0.047 \pm 0.005\)\\
167-317  & LV2 & 7.8 & \(0.305 \pm 0.025\) & \(0.81 \pm 0.28\) & \(1.50 \pm 0.1\) & \(0.085 \pm 0.015\) & 0.1--0.2 & \(13 \pm 13\) & \(0.018 \pm 0.001\) & \(0.225 \pm 0.005\)\\
         & LV2b& 7.0 & \(0.097 \pm 0.002\) & \(2.00 \pm 0.62\) & \(1.63 \pm 0.08\) & \(0.008 \pm 0.003\) & 0.8--0.8 & \(28 \pm 13\) & \(0.018 \pm 0.002\) & \(0.078 \pm 0.012\)\\
163-317  & LV3 & 6.9 & \(0.334 \pm 0.002\) & \(1.81 \pm 0.11\) & \(1.81 \pm 0.15\) & \(0.075 \pm 0.025\) & 0.6--0.8 & \(35 \pm 5\) & \(0.018 \pm 0.001\) & \(0.205 \pm 0.025\)\\
161-324  & LV4 & 6.2 & \(0.186 \pm 0.002\) & \(2.59 \pm 0.24\) & \(2.05 \pm 0.07\) & \(0.040 \pm 0.014\) & 0.8--1.0 & \(18 \pm 12\) & \(0.014 \pm 0.001\) & \(0.160 \pm 0.028\)\\
168-323  & LV5 & 9.4 & \(0.213 \pm 0.002\) & \(1.57 \pm 0.07\) & \(1.60 \pm 0.07\) & \(0.055 \pm 0.005\) & 0.2--0.4 & \(20 \pm 5\) & \(0.022 \pm 0.001\) & \(0.190 \pm 0.010\)\\
\bottomrule
\end{tabular}
\begin{minipage}{0.95\linewidth}
  Notes --
%
  Col.~(1): Source ID \citep{ODell:1994a}.
%
  Col.~(2): Alternative name of source.
% 
  Col.~(3): Projected distance from \thC{}, arcseconds.
%
  Col.~(4): Apparent shell outer radius along axis, normalized to
  projected distance, with \(\pm 1\sigma\) uncertainties, determined
  from circle fits described in \S~\ref{sec:methodology}.
% 
  Col.~(5): Apparent shell radius of curvature, normalized to radius
  along axis, with \(\pm 1\sigma\) uncertainties, determined from
  circle fits described in \S~\ref{sec:methodology}.
% 
  Col.~(6): As Col.~(5) but applying the additional requirement that
  the proplyd surface brightness from model fits should agree with the
  theoretical prediction.
%
  Col.~(7): Proplyd-to-O~star wind momentum ratio (see \S~\ref{sec:crw-scenario}). 
% 
  Col.~(8): Proplyd wind anisotropy factor.
% 
  Col.~(9): Inclination to plane of sky, degrees.
% 
  Col.~(10): True distance from \thC{}, parsecs.
%
  Col.~(11): True shell radius along axis, normalized to distance.

\end{minipage}
\end{table*}
%Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with fixed wind's momentum ratio $\beta$. 
%The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored 
%curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. The observational measurements are accompained with radial bars which represents the variations 
%with a fraction of the shell's marks removed. Proplyds with less data marks or high asymmetry show higher deviations in the measurements.
